Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-06 paper.tex
transaction level property

  \item \textbf{Co-verification Tools:} We present an automatic HW/SW co-verification tool called, \hwcbmcv,
    which follows the monolithic verification technique.  Our path-based 
    approach is implemented in a tool called, \verifox. Both tools can handle
    co-designs where the hardware is implemented in Verilog RTL (IEEE
    SystemVerilog 2005 standards) and the firmware is  
    specified in ANSI-C (C89, C99 standards).  We distribute the HW/SW 
    co-verification tools, \hwcbmcv and \verifox, along with our co-design 
    benchmarks in Verilog RTL and C models 
    here~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.

@@

We verify several properties of the FW-HW interactions of UART IP. 
In Scenario~A and scenario~B, we verified whether

@@

In both of the
configurations, \verifox is able to prune the receiver logic since the

@@

\textbf{\emph{About the firmware:}}
%
The firmware initiates the operation in the SoC by first writing to an
initial memory-mapped register.  The firmware implements Linux-style $inb()$
and $outb()$ functions calls, which are used to communicate with the HW
ports.  The firmware writes a sequence of non-deterministic data to the XRAM
port and then reads the data from the same port.  The cryptographic
accelerators use direct memory access to fetch the data from the external
memory.  The completion of the operation is determined by polling the
appropriate memory-mapped registers in the FW.

@@

\textbf{\emph{Discussion of the result:}}
%
Table~\ref{table:SoC} gives the runtimes for bounded safety proofs of 
FW-HW interaction properties of the SoC.  Column~1 in
Table~\ref{table:SoC} gives the name of the scenario -- transmission with
interrupt (data\_transfer).  Column~2 report the maximum loop bound in the
firmware.  Column~3~and~4 present the co-verification times using \hwcbmcv
at the bit-level and word-level.  Columns~[5-8] report the
verification times for the corresponding unified program netlist model using
\cbmcv, \klee, \textsc{symbiotic} and \verifox, respectively.

\textbf{\emph{Safety properties:}}
%
We verify several safety properties for the FW-HW interactions.  We check
whether the acknowledgment for data transmission and data reception arrives
from the micro-controller in the correct cycle.  We verify whether the
non-deterministic data transmitted through $outb()$ is the same
the data received through $inb()$.  We also verify that
reading/writing to the appropriate memory-mapped registers produce the
correct result during the data transmission phase.\\ \textbf{\emph{Detecting
SoC bugs:}} We found a control-path bug in the SoC design.  The bug is
manifested when memory arbiter hardware wrongly arbitrates the port
selection thereby forcing the write strobe for the external RAM to be LOW. 
This violates the data transfer protocol in the SoC design.

The result in Table~\ref{table:SoC} shows that \verifox is approximately
$5\times$ faster than \hwcbmcv and $6\times$ faster than \cbmcv for proving
safety.  For detecting bugs, the speedup is $72\times$ and $75\times$ for
\verifox over \hwcbmcv and \cbmcv.  However, \verifox marginally wins over
other path-based tools such as \symbiotic and \klee for safety proofs as
well as finding bugs. The result shows that the verification times for all
path-based techniques are comparable.  The reason for better scalability for
symbolic execution tools compared to \hwcbmcv is attributed to the path-based 
exploration strategy combined with eager path pruning and incremental SAT
solving. The FW exercises only the micro-controller
and transfer sequence of bytes to the XRAM port bypassing peripherals
connected to other ports such as hardware accelerator.  This scenario
allows path-based tools to prune the logic for accelerator which otherwise
could not have been removed by simple property-driven slicing of the
program netlist.  It is important to note that forward symbolic execution without
these optimizations timeout for all the benchmarks.

By contrast, \hwcbmcv is not able to prune the FW-HW transactions with
respect to a scenario due to monolithic BMC based approach.  Hence, \hwcbmcv
passes extremely complex formulas to the underlying solver, which often
contain irrelevant logic with respect to a particular scenario and are
therefore difficult to solve.

@@

In this paper, we presented a novel HW/SW co-verification tool, \verifox,
for C-based FW and hardware models given in Verilog RTL.  We presented a
notion of transaction in joint RTL and FW models.  We showed that the
interaction pattern between FW and HW transactions can be exploited to
generate a unified program netlist model.  To this end, we presented a
path-based symbolic execution technique to automatically infer
scenario/transaction pairs from a program netlist.  Our general observation
is that monolithic BMC based approaches cannot exploit these interactions
and thus generate very complex formulas, which are difficult to solve. 
Owing to specific optimizations in \verifox such as eager path pruning
combined with incremental SAT solving, we experimentally show that \verifox
is an order of magnitude faster than the state-of-the-art HW/SW
co-verification tool, \hwcbmcv.  We demonstrate applicability of our
approach for proving safety as well as finding FW-HW bugs for a UART IP and
a SoC design.  In the future, we plan to extend our framework to FW-HW
models that exhibit further interaction patterns.

>>>>

  \item \textbf{Co-verification Tools:} We present an automatic HW/SW co-verification tool called, \hwcbmcv,
    which follows the monolithic verification technique.  Our path-based 
    approach is implemented in a tool called, \verifox. Both tools can handle
    co-designs where the hardware is implemented in Verilog RTL (IEEE
    SystemVerilog 2005 standards) and the firmware is  
    specified in ANSI-C (C89, C99 standards).  We distribute the HW/SW 
    co-verification tools, \hwcbmcv and \verifox, along with our co-design 
    benchmarks in Verilog RTL and C models 
    here~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.\rmcmt{check
    link}

@@

We verify a total of~17 transaction level properties and~22 component level 
properties of the UART IP.  Table~\ref{table:safe} reports some of the
representative properties.  In Scenario~A and scenario~B, we verified whether

@@

In both of the configurations, \verifox is able to prune the receiver logic since the

@@

\textbf{\emph{About the firmware:}}
%
The FW initiates the operation in the SoC by first writing to an
initial memory-mapped register.  The FW implements Linux-style $inb()$
and $outb()$ functions calls, which are used to communicate with the HW
ports.  The FW writes a sequence of non-deterministic data to the XRAM
port and then reads the data from the same port.  The cryptographic
accelerators use direct memory access to fetch the data from the external
memory.  The completion of the operation is determined by polling the
appropriate memory-mapped registers in the FW.

@@

\textbf{\emph{Discussion of the result:}}
%
Table~\ref{table:SoC} gives the runtimes for bounded safety proofs of 
co-design properties of the SoC.  Column~1 in
Table~\ref{table:SoC} gives the name of the scenario -- transmission with
interrupt (data\_transfer).  Column~2 report the maximum loop bound in the 
FW.  Column~3~and~4 present the co-verification times using \hwcbmcv
at the bit-level and word-level, respectively.  Columns~5 report the
verification time using \verifox.

\textbf{\emph{Safety properties:}}
%
We verify a total of 7 transaction level propertes and 12 
component level properties for the SoC co-design.  Due to space 
limitations, we describe some representative properties.  We check
whether the acknowledgment for data transmission and data reception arrives
from the micro-controller in the correct cycle.  We verify whether the
non-deterministic data transmitted through $outb()$ is the same
the data received through $inb()$.  We also verify that
reading/writing to the appropriate memory-mapped registers produce the
correct result during the data transmission phase.\\

\textbf{\emph{Detecting SoC bugs:}} We found one critical \emph{control bug} 
in the SoC design.  The bug is manifested when memory arbiter hardware 
wrongly arbitrates the port selection thereby forcing the write strobe 
for the external RAM to be LOW.  This violates the data transfer protocol 
in the SoC design.

The result in Table~\ref{table:SoC} shows that \verifox is approximately
$5\times$ faster than \hwcbmcv for proving safety.  For detecting bugs, 
the speedup is $72\times$ for \verifox over \hwcbmcv.

\textbf{\emph{Monolithic versus Path-based:}}
The reason for better scalability of \verifox compared to 
\hwcbmcv is attributed to the path-based exploration strategy combined 
with eager path pruning and incremental SAT solving.  In the case of SoC, 
the FW exercises only the micro-controller and transfer sequence of bytes to the XRAM port 
bypassing peripherals connected to other ports such as hardware accelerator.  
This scenario allows path-based exploration techniques to prune the logic for
accelerator.  It is important to note that forward symbolic execution without
these optimizations timeout for all the benchmarks.

By contrast, \hwcbmcv is not able to prune the irrelevant transactions with
respect to a scenario due to monolithic BMC based approach.  Hence, \hwcbmcv
passes extremely complex formulas to the underlying solver, which often
contain irrelevant logic and are therefore difficult to solve.

@@

In this paper, we presented a novel HW/SW co-verification tool, \verifox,
for C-based FW and hardware models given in Verilog RTL.  We presented a
notion of transaction in joint RTL and FW models.  We showed that the
interaction pattern between FW and HW transactions can be exploited to
generate a unified co-verification model.  To this end, we presented a
path-based symbolic execution technique to automatically infer
scenario/transaction pairs from a co-verification model.  Our general observation
is that monolithic BMC based approaches cannot exploit these interactions
and thus generate very complex formulas, which are difficult to solve. 
Owing to specific optimizations in \verifox such as eager path pruning
combined with incremental SAT solving, we experimentally show that \verifox
is an order of magnitude faster than the state-of-the-art HW/SW
co-verification tool, \hwcbmcv.  We demonstrate applicability of our
approach for proving safety as well as finding FW-HW bugs for a UART IP and
a SoC design.  In the future, we plan to extend our framework to FW-HW
models that exhibit further interaction patterns.
